Visualize ukb whole genome, s40.22

### 2021-01-17 analysis/simulation-susieI-ukbWG-gtex.adipose_s40.22.Rmd
snakemake workflow using ctwas package

ncausal_plot <- function(pipfs, format = "susie", main = "PIP"){
  df <- NULL
  for (i in 1:length(pipfs)) {
    res <- fread(pipfs[i], header = T)
    res <- data.frame(res[res$type  =="gene", ])
    res$runtag <- i
    if (format == "susie"){
       res <- rename(res, c("susie_pip" = "pip"))
    } else if (format == "SER"){
       res <- rename(res, c("SERpip" = "pip"))
    }
    res <- res[complete.cases(res),]
    df <- rbind(df, res)
  }

@@

  # df$ifcausal <- mapvalues(df$ifcausal, from=c(0,1),to=c("darkgreen", "salmon"))
  # plot(df$TWAS.p, df$pip, col = df$ifcausal, main = main, xlab = "-log10(TWAS p value)", ylab = "PIP")
  # 
  df$ifcausal <- mapvalues(df$ifcausal, from=c(0,1), to=c("Non causal", "Causal"))
  fig <- plot_ly(data = df, x = ~ TWAS.p, y = ~ pip, color = ~ ifcausal,
                 colors = c( "salmon", "darkgreen"), type ="scatter", text = ~ paste("Name: ", paste0(runtag,":",name),
                                                                   "\nChr: ", chr,  "\nPos:", pos))

@@

```{r scatter1susie, fig.height=4, fig.width=8}
par(mfrow=c(1,2))
f1 <- scatter_plot_PIP_p(susieIfs2[1:5], gwasfs[1:5], pipformat = "susie", main = "low power")
f2 <- scatter_plot_PIP_p(susieIfs2[6:10], gwasfs[6:10], pipformat = "susie", main = "high power")
```

@@

```{r scatter6susie, fig.height=4, fig.width=8}
par(mfrow=c(1,2))
f1 <- scatter_plot_PIP_p(susieIfs2[1:5], gwasfs[1:5], pipformat = "susie", main = "low power")
f2 <- scatter_plot_PIP_p(susieIfs2[6:10], gwasfs[6:10], pipformat = "susie", main = "high power")
```

@@

```{r scatter8susie, fig.height=4, fig.width=8}
par(mfrow=c(1,2))
f1 <- scatter_plot_PIP_p(susieIfs2[1:5], gwasfs[1:5], pipformat = "susie", main = "low power")
f2 <- scatter_plot_PIP_p(susieIfs2[6:10], gwasfs[6:10], pipformat = "susie", main = "high power")
```

@@

```{r scatter9susie, fig.height=4, fig.width=8}
par(mfrow=c(1,2))
f1 <- scatter_plot_PIP_p(susieIfs2[1:5], gwasfs[1:5], pipformat = "susie", main = "low power")
f2 <- scatter_plot_PIP_p(susieIfs2[6:10], gwasfs[6:10], pipformat = "susie", main = "high power")
```

@@

```{r scatter10susie, fig.height=4, fig.width=8}
par(mfrow=c(1,2))
f1 <- scatter_plot_PIP_p(susieIfs2[1:5], gwasfs[1:5], pipformat = "susie", main = "low power")
f2 <- scatter_plot_PIP_p(susieIfs2[6:10], gwasfs[6:10], pipformat = "susie", main = "high power")
```

@@

@@

@@

```{r scatter1ser, fig.height=4, fig.width=8}
par(mfrow=c(1,2))
f1 <- scatter_plot_PIP_p(susieIfs2[1:5], gwasfs[1:5], pipformat = "SER", main = "low power")
f2 <- scatter_plot_PIP_p(susieIfs2[6:10], gwasfs[6:10], pipformat = "SER", main = "high power")
```

@@

```{r scatter7ser, fig.height=4, fig.width=8}
par(mfrow=c(1,2))
f1 <- scatter_plot_PIP_p(susieIfs2[1:5], gwasfs[1:5], pipformat = "SER", main = "low power")
f2 <- scatter_plot_PIP_p(susieIfs2[6:10], gwasfs[6:10], pipformat = "SER", main = "high power")
```

>>>>

ncausal_plot <- function(pipfs, format = "susie", main = "PIP"){
  df <- NULL
  for (i in 1:length(pipfs)) {
    res <- fread(pipfs[i], header = T)
    res <- data.frame(res[res$type  =="gene", ])
    res$runtag <- i
    if (format == "susie"){
       res <- rename(res, c("susie_pip" = "pip") )
    } else if (format == "SER"){
       res <- rename(res, c("SERpip" = "pip"), )
    }
    res <- res[complete.cases(res),]
    df <- rbind(df, res)
  }

@@

  df$ifcausal <- mapvalues(df$ifcausal, from=c(0,1),to=c("darkgreen", "salmon"))
  plot(df$TWAS.p, df$pip, col = df$ifcausal, main = main, xlab = "-log10(TWAS p value)", ylab = "PIP")

  # df$ifcausal <- mapvalues(df$ifcausal, from=c(0,1), to=c("Non causal", "Causal"))
  # fig <- plot_ly(data = df, x = ~ TWAS.p, y = ~ pip, color = ~ ifcausal,
  #                colors = c( "salmon", "darkgreen"), type ="scatter", text = ~ paste("Name: ", paste0(runtag,":",name),
  #                                                                  "\nChr: ", chr,  "\nPos:", pos))

@@

@@

@@

@@

@@

@@

```{r scatter3susiefl, fig.height=4, fig.width=8}
par(mfrow=c(1,2))
f1 <- scatter_plot_PIP_p(susieIfs2[1:5], gwasfs[1:5], pipformat = "susie", main = "low power")
f2 <- scatter_plot_PIP_p(susieIfs2[6:10], gwasfs[6:10], pipformat = "susie", main = "high power")
```

@@

```{r scatter4susiefl, fig.height=4, fig.width=8}
par(mfrow=c(1,2))
f1 <- scatter_plot_PIP_p(susieIfs2[1:5], gwasfs[1:5], pipformat = "susie", main = "low power")
f2 <- scatter_plot_PIP_p(susieIfs2[6:10], gwasfs[6:10], pipformat = "susie", main = "high power")
```

@@

@@

### 2021-01-17 analysis/simulation-susieI-ukbWG-gtex.adipose_visual.Rmd
snakemake workflow using ctwas package

plot_all <- function(SERf, phenof, chrom, ldres = NULL){
  a <- fread(SERf, header =T)
  load(phenof)

  a <- a[a$chr == chrom,]

@@

  colnames(a)[colnames(a) == "SERpip"] <-  "susiePIP"
  colnames(a)[colnames(a) == "pos"] <-  "p0"

  a[, "PVALUE"] <- -log10(a[, "pvalue"])
  a[, "lbf"] <- log10(exp(a[, "lbf"]))

@@

  fig1 <- plot_susie_pip(dt.gene) 
  fig2 <- plot_lbf(dt.gene)
  fig3 <- plot_p(dt.gene)

  fig4 <- plot_susie_pip(dt.snp)
  fig5 <- plot_lbf(dt.snp) 
  fig6 <- plot_p(dt.snp) %>% layout( plot_bgcolor='#EFF6FC')

  fig <- subplot(fig1, fig2, fig3, fig4, fig5, fig6, nrows=6, shareX = T, titleY = T)

  fig <- fig %>% layout(autosize = F, width = 600, height = 800, margin = 0.02,
                        xaxis = list(title = "Genomic position"))

@@

```{r sim 1-3-17, out.width = "98%", out.height="95%"}
chrom <- 13
tag <- "20201001-1-2"
pipfile <-  paste0(outputdir, tag, ".config6.SERI.txt")
phenof <- paste0(simdatadir, "simu_", tag, "-pheno.Rd")
plot_all(pipfile, phenof, chrom)
```

>>>>

plot_all <- function(susief, pf, phenof, chrom, ldres = NULL){
  a <- fread(susief, header =T)
  b1 <- fread(paste0(pf, ".snpgwas.txt.gz"), header =T)
  b2 <- fread(paste0(pf, ".exprgwas.txt.gz"), header =T)
  b <- rbind(b1, b2)
  setnames(b, old = c('X.CHROM', 'PVALUE', 'MARKER_ID'),
         new = c("chr", 'pvalue', 'name'))

  load(phenof)

  a <- a[a$chr == chrom,]
  b <- b[b$chr == chrom,]

  a <- merge(a, b, by = "name", all.x =T)

@@

  colnames(a)[colnames(a) == "susie_pip"] <-  "susiePIP"
  colnames(a)[colnames(a) == "pos"] <-  "p0"

  a[, "PVALUE"] <- -log10(a[, "pvalue"])

@@

  fig1 <- plot_susie_pip(dt.gene)  # %>%  add_trace(p, x = list(1), y = list(1), name = " ", showlegend = F)
  # fig2 <- plot_lbf(dt.gene)
  fig3 <- plot_p(dt.gene)

  fig4 <- plot_susie_pip(dt.snp)
  # fig5 <- plot_lbf(dt.snp) 
  fig6 <- plot_p(dt.snp) %>% layout( plot_bgcolor='#EFF6FC')

  fig <- subplot(fig1, fig3, fig4, fig6, nrows=4, shareX = T, titleY = T)

  fig <- fig %>% layout(autosize = F, width = 600, height = 500, margin = 0.02,
                        xaxis = list(title = "Genomic position"))

@@

```{r sim 1-3-17, out.width = "98%", out.height="95%"}
chrom <- 2
tag <- "20201001-2-5"
susief <-  paste0(outputdir, tag, ".config16.flrerun.susieI.txt")
pf <- paste0(simdatadir, tag)
phenof <- paste0(simdatadir, "simu_", tag, "-pheno.Rd")
plot_all(susief, pf, phenof, chrom)
```
